Schema Evolution in Interactive Programming Systems

### 2024-08-28 paper.tex
fix typos

\begin{itemize}
\item \emph{Schema} -- structure program data and determine aspects of code. A change in schema
  requires a corresponding change in data and code. Schema may be explicit (database schema, type declarations)
  or implicit (expected shape of data structures or a document).
\item \emph{Data} -- information stored by the program. Data may be more permanent (data in a
  database) or less permanent (state in live programming). When scheam evolve, data needs to be
  updated or (in case of transient state) discarded.
\item \emph{Code} -- or program logic, but not including source code that defines schema.
  When schema evolve, code needs to change to consume/produce data of the correct shape.
\end{itemize}

>>>>

\begin{itemize}
\item \emph{Schema} -- structures program data and determines aspects of code. A change in schema
  requires a corresponding change in data and code. Schema may be explicit (database schema, type declarations)
  or implicit (expected shape of data structures or a document).
\item \emph{Data} -- information stored by the program. Data may be more permanent (data in a
  database) or less permanent (state in live programming). When schemas evolve, data needs to be
  updated or (in case of transient state) discarded.
\item \emph{Code} -- or program logic, but not including source code that defines schema.
  When schemas evolve, code needs to change to consume/produce data of the correct shape.
\end{itemize}
